Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-05-31 SecDev21/paper.tex
Correct sentences

\todo[inline]{Is this part good enough or does it need to be rewritten?}

The soundness of our verificatin requires all the contracts to be correct, in particular this is true for the contract of \spark{TCP_Process_One_Segment}.
Get this contract can be done by rewriting in SPARK the part that processes the
incoming segments, but this is out of the scope of this work.
Instead, we have opted for the use of symbolic execution on the
original CycloneTCP C code.
Symbolic execution is a mean to execute programs with symbolic values rather
than concrete values. Symbolic execution has already been successfully
used with other verification methods.
Indeed, in~\cite{vanoverberghe2008using} the authors present how to use symbolic
execution to improve deductive verification, and in~\cite{kassios2012comparing}
the authors explain that symbolic execution can be good at inferring contracts.
For our work, KLEE\footnote{\url{https://klee.github.io}} has been used.
It is built on top of LLVM as it takes LLVM
bytecode in input and works well with C code thanks to a very simple interface.

@@

The TCP protocol implies a specific order such that the user can call the API's
functions without breaking the functional specification of the protocol. This
order also is being conveyed by the protocol's state machine given in
figure~\ref{Fig:statemachine}.
Ada's preconditions and postconditions are a powerful tool to express such inter-function
dependencies, while SPARK technology can be used to guarantee that the
assertions always hold. Thus, preconditions and postconditions were introduced to model
a partial order on the calls to the API's functions.

@@

Simplified contracts extracted from our library are reproduced in
figure~\ref{fig:functionorder}. If no error occurs, the function
\spark{Socket_Connect} sets \spark{Sock.S_Remote_Ip_Addr} to
\spark{Remote_Ip_Addr} which is supposed to be
initialized when the function is called. \spark{Socket_Send} requires to be
called with a socket not null such that its field \spark{Remote_Ip_Addr} is
initialized. The only way to ensure that the precondition hold is to
call \spark{Socket_Connect} before \spark{Socket_Send}.
The tool GNATprove can statically find if a call to \spark{Socket_Send}
is not preceded by a call to \spark{Socket_Connect}.

>>>>

The soundness of our verification requires all the contracts to be correct, in particular this is true for the contract of \spark{TCP_Process_One_Segment} that is used to prove the function \spark{TCP_Wait_For_Events}.
Getting this contract can be done by rewriting in SPARK the part that processes the
incoming segments, but this is out of the scope of this work.
Instead, we have opted for the use of symbolic execution on the
original CycloneTCP C code.
Symbolic execution is a mean to execute programs with symbolic values rather
than concrete values. Symbolic execution has already been successfully
used with other verification methods.
Indeed, in~\cite{vanoverberghe2008using} the authors present how to use symbolic
execution to improve deductive verification, and in~\cite{kassios2012comparing}
the authors explain that symbolic execution can be good at inferring contracts.
For our work, KLEE\footnote{\url{https://klee.github.io}} has been used.
It is built on top of LLVM as it takes LLVM
bytecode in input and works well with C code thanks to a very simple interface.

@@

The TCP protocol implies a specific order such that the user can call the API's
functions without breaking the functional specification of the protocol. This
order also is being conveyed by the protocol's state machine given in
\Cref{Fig:statemachine}.
Ada's preconditions and postconditions are a powerful tool to express such inter-function
dependencies, while SPARK technology can be used to guarantee that the
assertions always hold. Thus, preconditions and postconditions were introduced to model
a partial order on the calls to the API's functions.

@@

Simplified contracts extracted from our library are reproduced in
\Cref{fig:functionorder}. If no error occurs, the function
\spark{Socket_Connect} sets \spark{Sock.S_Remote_Ip_Addr} to
\spark{Remote_Ip_Addr} which is supposed to be
initialized when the function is called. \spark{Socket_Send} requires to be
called with a socket not null such that its field \spark{Remote_Ip_Addr} is
initialized. The only way to ensure that the precondition hold is to
call \spark{Socket_Connect} before \spark{Socket_Send}.
The tool GNATprove can statically find if a call to \spark{Socket_Send}
is not preceded by a call to \spark{Socket_Connect}.
